Nowadays customers are faced with a vast choice in products, services and content. However, consumers don't want to waste time manually filtering through these choices. Recommender systems (RS) overcome this by providing personalized recommendations that suit a particular users' tastes. They are employed by tech companies in many distinct areas to predict ratings or preferences of their users. Spotify uses them to create personalized playlists. Amazon uses them to suggest products that consumers may wish to purchase. Facebook uses them to recommend pages and people to follow. In this paper I will discuss the best practices in deep learning and propose tower architecture network that incorporates extra content information into the model. I will also discuss the design choices that went into creation of a modern scalable web application to host and serve the recommendations. Later I will compare the effectiveness of the algorithm with state of the art matrix factorization methods. The experiments on the movieLens dataset show a decrease of 4.77\% and 5.86\% in RMSE compared to SVD and NMF factorization algorithms.

\subsection{Dataset}
The dataset used as the basis for the recommendation engine is the movie lens 20m dataset, put together by the Grouplens research group at the University of Minnesota (\citet{movielens}).
This is an explicit feedback dataset, where users manually assigned ratings to movies. The characteristics of this dataset are the following.
\begin{itemize}
    \item 20000263 ratings on a scale of 0.5-5 in 0.5 increments
    \item 27278 movies having been rated at least once
    \item 138493 users that have rated at least 20 movies
    \item 465564 tags about movies
\end{itemize}
The dataset is split into different files of which I am only using the ratings, movies and links files. They are all available in comma-separated value format.
\begin{itemize}
    \item Ratings file - userId, movieId, rating, and timestamp
    \item Movies file - movieId, title, genre
    \item Links file - movieId, imdbId and tmdbId
\end{itemize}
The ratings file is the main dataset which will be used for collaborative filtering. The movies file is used to incorporate genre content data into the model. The links file provides useful ids from IMDB, a movie reviews website. These ids are used for webs-scrapping, to make available extra content for the demo web application..

% \begin{center}
%     \begin{tabular}{||c c c c||} 
%     \hline
%     userId & movieId & rating & timestamp \\ [0.5ex] 
%     \hline\hline
%     57772 & 3861 & 4.0 & 982690041 \\ 
%     \hline
%     122521 & 1411 & 2.0 & 1001957487 \\
%     \hline
%     22759 & 46578 & 4.0 & 1216540196 \\
%     \hline
%     92812 & 1206 & 2.5 & 1118792437 \\ [1ex] 
%     \hline
%    \end{tabular}
% \captionof{table}{Rating file}\label{ratingsFile}
% \end{center}

% \begin{center}
%     \begin{tabular}{||c c c||} 
%     \hline
%     movieId & title & genres \\ [0.5ex] 
%     \hline\hline
%     106749 & Mr. Morgan's Last Love (2013) & Comedy\textbar Drama \\ 
%     \hline
%     2 & Jumanji (1995) & Adventure\textbar Children\textbar Fantasy\\
%     \hline
%     91169 & Easier with Practice (2009) & Drama\textbar Romance \\
%     \hline
%     106879 & Fright Night 2: New Blood (2013) & Horror \\ [1ex] 
%     \hline
%    \end{tabular}
% \captionof{table}{Movie file}\label{moviesFile}
% \end{center}

% \begin{center}
%     \begin{tabular}{||c c c||} 
%     \hline
%     movieId & imdbId & tmdbId \\ [0.5ex] 
%     \hline\hline
%     6 & 0113277 & 949 \\ 
%     \hline
%     206 & 0114805 & 77350 \\
%     \hline
%     71466 & 1174730 & 28053 \\
%     \hline
%     96834 & 2343601 & 111174 \\ [1ex] 
%     \hline
%    \end{tabular}
% \captionof{table}{Links file}\label{linksFile}
% \end{center}
